Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-10-25 manuscript/manuscript.Rmd
Working on methods section. First set of questions looks good. Need to add interpretations to second set of plots.

A few paragraphs about the context of what has been done with conjoint analysis within the political and/or public policy field.

>>>>

Conjoint analysis shows which components of a choice hold the most weight. Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields. Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess consumer perceptions of political communications. Conjoint is key in political research because it captures multidimensional causal relations.

Knudsen and Johannesson (2018) argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgement of credibility. Public policy research would benefit from conjoint analysis for the same reasons.
